Optimal (Multiway) Spatial Joins

### 2024-05-31 msj.tex

Again, sweep a horizontal line $\ell$ from $y = -\infty$ to $y = \infty$. At all times, we maintain the set $R_\ell$ of rectangles in $R$ that intersect with $\ell$. Let $S_\ell$ be the set of x-ranges of the rectangles in $R_\ell$; we store $S_\ell$ in a PST $\T$. Specifically, when $\ell$ hits the bottom (resp., top) edge of a rectangle $r = [x_1, x_2] \times [y_1, y_2]$ of $R$, we insert (resp., delete) $[x_1, x_2]$ into (resp., from) $\T$, which can be done in $O(\log n)$ time. The rectangle $r$ will be referred to as the {\em host} of $[x_1, x_2]$ and is stored together with $[x_1, x_2]$ in $\T$.

@@

Overall, each rectangle of $R$ necessitates one insertion and one deletion in $\T$. All these insertions and deletions take $O(n \log n)$ time in total. Each segment $h$ of $H$ performs a containment query on $\T$, which has a cost of $O(\log n + K_h)$. All these queries demand a total cost of $O(n \log n + \sum_h K_h)$. However, unlike the detection version, the sum $\sum_h K_h$ is equal to the total size of $\cross_H(r)$ for all the $r \in R$. The total size is equivalent to $\out$.

>>>>

Again, sweep a horizontal line $\ell$ from $y = -\infty$ to $y = \infty$. At all times, we maintain the set $R_\ell$ of rectangles in $R$ that intersect with $\ell$. Let $S_\ell$ be the set of x-ranges of the rectangles in $R_\ell$; we store $S_\ell$ in a PST $\T$. Specifically, when $\ell$ hits the bottom (resp., top) edge of a rectangle $r = [x_1, x_2] \times [y_1, y_2]$ of $R$, we insert (resp., delete) $[x_1, x_2]$ into (resp., from) $\T$, which can be done in $O(\log n)$ time. Again, the rectangle $r$ --- the host of $[x_1, x_2]$ --- is stored together with $[x_1, x_2]$ in $\T$.

@@

Overall, each rectangle of $R$ necessitates one insertion and one deletion in $\T$. All these insertions and deletions take $O(n \log n)$ time in total. Each segment $h$ of $H$ performs a containment query on $\T$, which has a cost of $O(\log n + K_h)$. All these queries demand a total cost of $O(n \log n + \sum_h K_h)$. However, unlike the detection version, the sum $\sum_h K_h$ here is equal to the total size of $\cross_H(r)$ for all the $r \in R$. The total size is equivalent to $\out$.
